### 2015-06-01 writing/SNLI paper/entailment_eval.tex
Added SICK classifier results.

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\textbf{System} & \b{Our corpus} & \b{SICK} & \b{RTE-3} \\
\midrule
\t{Edit Distance Based}        & \t{71.9} & \t{65.4} & \b{61.9} \\
\t{Classifier Based}           & \b{72.2} & \b{71.4} & \t{61.5} \\
%\midrule
%\t{Classifier Based (3-class)} & \t{??.?} & \t{65.6} & \t{} \\
%\t{Transformation Based} & \t{36.0} & \t{76.7} & \t{56.4} \\
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
2-class accuracy for two entailment algorithms included in the
  Excitement Open Platform.
%All RTE results are 2-class accuracy.
%The transformation-based model allows for 3-class predictions on our
%  corpus and SICK; these are reported in the last row.
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\b{System} & \b{Train} & \b{Test} \\
\midrule
\t{Lexicalized}            & \t{99.7}  & \b{78.2} \\ % & \t{78.7}
\t{Unigrams Only}          & \t{93.1} & \t{71.6} \\ % & \t{72.2}
\t{Unlexicalized}          & \t{49.4} & \t{50.4} \\ % & \t{50.1} % Last value was 50.39; rounded for consistency.
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
3-class accuracy on our dataset.
Ablation results are reported for models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
}
\end{table}
%
% END BOW RESULTS TABLE
%

>>>>

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\b{System} & \b{Our corpus} & \b{SICK} & \b{RTE-3} \\
\midrule
\t{Edit Distance Based}        & \t{71.9} & \t{65.4} & \b{61.9} \\
\t{Classifier Based}           & \b{72.2} & \b{71.4} & \t{61.5} \\
%\midrule
%\t{Classifier Based (3-class)} & \t{??.?} & \t{65.6} & \t{} \\
%\t{Transformation Based} & \t{36.0} & \t{76.7} & \t{56.4} \\
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
2-class accuracy for two entailment algorithms included in the
  Excitement Open Platform.
%All RTE results are 2-class accuracy.
%The transformation-based model allows for 3-class predictions on our
%  corpus and SICK; these are reported in the last row.
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c}
\toprule
\b{System}	 & \multicolumn{2}{c}{\b{Our corpus}} & \b{SICK}\vspace{-0.5mm}\\
 & \b{Train} & \b{Test} & \b{Test} \vspace{-0.5mm}\\
\midrule
\t{Lexicalized}            & \t{99.7}  & \b{78.2} & \b{77.3} \\ % & \t{78.7}
\t{Unigrams Only}          & \t{93.1} & \t{71.6} & \t{74.0} \\ % & \t{72.2}
\t{Unlexicalized}          & \t{49.4} & \t{50.4} & \t{69.4}\\ % & \t{50.1} % Last value was 50.39; rounded for consistency.
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
3-class accuracy on our dataset.
Ablation results are reported for models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
}
\end{table}
%
% END BOW RESULTS TABLE
%
